\documentclass[a4paper,12pt]{article}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{bm}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{algpseudocode}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{fontawesome}
\usepackage[skins]{tcolorbox}
\usepackage{algorithm}
\usepackage{listings}
\usepackage{placeins}  % For \FloatBarrier
\usepackage{float}     % For [H] option in figures/tables

\setlength{\textheight}{240mm}
\setlength{\textwidth}{160mm}
\setlength{\topmargin}{-15mm}
\setlength{\oddsidemargin}{-5mm}
\setlength{\evensidemargin}{-5mm}
\flushbottom
\setlength{\parindent}{0pt}
\setlength{\baselineskip}{17pt}
\setlength{\parskip}{3mm}
\setlength{\columnsep}{8mm}
\renewcommand{\baselinestretch}{1.35}

\definecolor{bg}{HTML}{e0f1ff}

\newtcolorbox{mybox}{colback=gray!10, colframe=blue!50!black, width=\textwidth, arc=3mm, auto outer arc, boxrule=0.5pt}

\usepackage{soul}

\begin{document}

\begin{mybox}
  \large

  \vspace{5mm}

  \textbf{Manuscript title:} Semantic-Guided Fusion Network for Multi-source Remote Sensing Image Classification

  \textbf{Article ID:} GRSL-01407-2026

  \textbf{Authors:} Yuwei Zhao, Chuanzheng Gong, Baogui Huan, Feng Gao, Junyu Dong and Qian Du
  
  \vspace{5mm}

\end{mybox}


\begin{center}
  \LARGE\bf Summary of Changes
\end{center}

Dear Editors,

We sincerely thank you for your time and invaluable feedback during the review process. Your expert comments have been instrumental in improving the quality and clarity of our manuscript. We have carefully addressed every point raised and made comprehensive revisions accordingly. All modifications in the revised manuscript are highlighted in red for easy reference. We have also added more detailed explanations and analyses to ensure that the manuscript is more comprehensive and informative.

We hope these revisions meet your expectations. Should further clarifications or adjustments be needed, we are fully committed to addressing them promptly. Your feedback is highly valued, and we are grateful for your support in helping us improve our work.

Sincerely,

Yuwei Zhao and Feng Gao \\

Ocean University of China

Email: gaofeng@ouc.edu.cn

\newpage

\include{bodies/response_AE}
\include{bodies/response_review1}
\include{bodies/response_review2}
\include{bodies/response_review3}

\end{document}
